PubCrawl: A Publication Search Engine

### 2012-05-18 report/paper.tex
Fix description of RankJoin
More information about user study

\documentclass[12pt]{article}
\usepackage{hyperref}
\setcounter{secnumdepth}{2} 
\title{PubCrawl: A Publication Search Engine}
\author{Frank Li (frankli@mit.edu) \\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}

@@

\begin{abstract}
Searching for documents ranked by relevance is a well-studied problem in
information retrieval. In particular, there are frameworks for estimating
relevance as a function of the content of the document and algorithms for
estimating relevance as a function of incoming links. However, further
specialization of these techniques is required to search a corpus of academic
papers. Academic papers are highly structured, lending additional weight to
matches which appear in important sections such as the title or abstract.
Contextual information changes the weight which should be contributed to cited
papers. Here we describe PubCrawl, a search engine built for the ACM Digital
Library available at \url{http://saw.csail.mit.edu:9000}. The system allows
users to weight the relative importance of matches in various sections of the
documents. We also implement a version of PageRank over the dataset. We
evaluate the system in user studies and find it produces comparable results to
other search engines.
\end{abstract}

@@

Here, we present PubCrawl, a new search engine for the ACM Digital Library
available at \url{http://saw.csail.mit.edu:9000}. The PubCrawl interface allows
users to submit search terms and assign relative weights to title, abstract,
and full text searches and PageRank. It uses the Django web framework for the
front-end interface and is backed by a Postgres database which stores metadata
(authors, venues, and citations) and a Lucene search index. Figure
\ref{interface} shows a screenshot of the interface.

\begin{figure}[p]
  \begin{center}
    \includegraphics[width=\textwidth]{images/interface}
  \end{center}
  \caption{PubCrawl user interface}
  \label{interface}
\end{figure}

@@

We acknowledge James Cowling, Adam Marcus, Eugene Wu for their assistance with
the user studies and Sam Madden for his feedback on our methods.

>>>>

\documentclass[12pt]{article}
\setcounter{secnumdepth}{2} 
\title{PubCrawl: A Publication Search Engine}
\author{Frank Li (frankli@mit.edu) \\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}

@@

\begin{abstract}
Searching for documents ranked by relevance is a well-studied problem in
information retrieval. In particular, there are frameworks for estimating
relevance as a function of the content of the document and algorithms for
estimating relevance as a function of incoming links. However, further
specialization of these techniques is required to search a corpus of academic
papers. Academic papers are highly structured, lending additional weight to
matches which appear in important sections such as the title or abstract.
Contextual information changes the weight which should be contributed to cited
papers. Here we describe PubCrawl, a search engine built for the ACM Digital
Library. The system allows users to weight the relative importance of matches
in various sections of the documents. We also implement a version of PageRank
over the dataset. We evaluate the system in user studies.
\end{abstract}

@@

PubCrawl is an online search website for the ACM Digital Library built with the
Django web framework. It is backed by a Postgres database which stores metadata
(authors, venues, and citations) and a Lucene search index. The PubCrawl
interface allows users to submit search terms and assign relative weights to
title, abstract, and full text searches and PageRank. Figure \ref{interface}
shows a screenshot of the interface.

\begin{figure}[bt]
  \begin{center}
    \includegraphics[width=\textwidth]{images/interface}
  \end{center}
  \caption{PubCrawl user interface}
  \label{interface}
\end{figure}

@@

We acknowledge Adam Marcus and Eugene Wu for their assistance with the user
studies.
